---
title: "Sandbox"
author: "Adelaida Barrera"
date: "11/30/2020"
output: html_document
---

# Trying to run topic model in full dfm 

```{r}

library(stm)

load("pruebas/full_feminists_dfm.RData")


#Make the quanteda dfm a stm corpus for running the model
stm_non_congress <- asSTMCorpus(non_congress_dfm)

# Getting info from the corpus
out <- prepDocuments(stm_non_congress$documents, 
                     stm_non_congress$vocab, 
                     stm_non_congress$meta)

# Running the structural topic model, defining 10 topics. 
model_topics_non_congress <- stm(documents = out$documents, 
              vocab = out$vocab, 
              K = 10, seed = 12345)

# Save the output for future plotting or analysis 
save(model_topics_non_congress, file = "model_topics_full")
```

#See what came out 

```{r}

plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = (1:3)) # or frex, lift, score
plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = (4:6)) 
plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = (7:9)) 
plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = 10)
 
```





##### Otros métodos para limpiar y procesar el dfm
##### Otros métodos #####

mycorpus <- Corpus(VectorSource(feminists$text))
mycorpus <- tm_map(mycorpus, removeWords, stopwords("spanish"))

# Remove URL
remove_url <- function(x) gsub("http[^[:space:]]*","",x)
mycorpus <- tm_map(mycorpus, content_transformer(remove_url))

# Remove anything other than spanish letters and space
remove_other <- function(x) gsub("[^[:alpha:][:space:]]*","", x) 
mycorpus <- tm_map(mycorpus, content_transformer(remove_other))
mycorpus <- tm_map(mycorpus, content_transformer(removePunctuation))
mycorpus <- tm_map(mycorpus, content_transformer(tolower))
mycorpus <- tm_map(mycorpus, stripWhitespace)
mycorpus <- tm_map(mycorpus, stemDocument)

mycorpus <- corpus(mycorpus)
mycorpus_dfm <- dfm(mycorpus)

#Create a sample to try analysis 
sample_tm <- dfm_sample(x = mycorpus_dfm, size = 1000, margin = "documents")
