---
title: "sentiment_analysis_feminists"
author: "Mariana Saldarriaga"
date: "12/18/2020"
output: html_document
---

```{r}
library(tidyverse)
library(quanteda)

# Dictionary 
sentimiento_d <- read.delim(file = "SpanishSentimentLexicons/fullStrengthLexicon.txt",
                          header = F,
                          col.names = c("word", "code", "sentiment", "score2"))

sentimiento_dict <- as.dictionary(sentimiento_d)
sentimiento_dict

# Dfm with dictionary by main occupation
sentimiento_dfm <- dfm(non_congress_corp,
                       groups = c("main_occupation"), 
                       dictionary = sentimiento_dict)

sentimiento_df <- convert(sentimiento_dfm, "data.frame") %>%
  gather(neg, pos, key = "Polarity", value = "Words")

# Graph sentiment output
sentiment_graph <- ggplot(sentimiento_df, aes(doc_id, Words, color = Polarity, group = Polarity)) +
  geom_line(size = 1) +
  ggtitle("Sentiment scores Gender Public Opinion Leaders on Twitter 
          (spanish sentiment dictionary online)") +
  xlab("Main occupation") +
  scale_color_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + xlab("")

sentiment_graph
```


```{r}
# Sentiment analysis with improved dictionnary includinc words in topic models. 

# Dictionary 
sentimiento_d_fem <- read.delim(file = "SpanishSentimentLexicon_feminist_discourse_v4.txt",
                          header = F,
                          col.names = c("word", "code", "sentiment", "topic"))

sentimiento_dict_fem <- as.dictionary(sentimiento_d_fem)
sentimiento_dict_fem

# Dfm with dictionary by main occupation
sentimiento_dfm2 <- dfm(non_congress_corp,
                       groups = c("main_occupation"), 
                       dictionary = sentimiento_dict_fem)

sentimiento_df2 <- convert(sentimiento_dfm2, "data.frame") %>%
  gather(neg, pos, key = "Polarity", value = "Words")

# Graph sentiment output
sentiment_graph2 <- ggplot(sentimiento_df2, aes(doc_id, Words, color = Polarity, group = Polarity)) +
  geom_line(size = 1) +
  ggtitle("Sentiment scores Gender Public Opinion Leaders on Twitter 
          (improved dictionary)") +
  xlab("Main occupation") +
  scale_color_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

sentiment_graph2
# Just by adding more positive words when talking about gender issues (old dictionary 456 to 530) the amount of positive words increase significantly. 
# Dictionary we added words that are in the topic model negative and positive, althought more positive. 
# Improve dictionaries
# Make sense journalists use more postive words as activists policy maker, and writers. 
```

# NRC dictionary
```{r}
library(quanteda)
library(readtext)
library(gridExtra)
library(ggplot2)
library(syuzhet)
library(reshape2)

# We get nrc dictionary (7 sentiments and also in Spanish)
dictionary_nrc <- get_sentiment_dictionary(dictionary = 'nrc', language = "spanish")
str(dictionary_nrc)

# Clean column text from non_congress data Twitter data base
corpus_sentim <- Corpus(VectorSource(non_congress$text))
corpus_sentim <- tm_map(corpus_sentim, removeWords, stopwords("spanish"))

# Remove URL
remove_url <- function(x) gsub("http[^[:space:]]*","",x)
corpus_sentim <- tm_map(corpus_sentim, content_transformer(remove_url))

# Remove anything other than spanish letters and space
remove_other <- function(x) gsub("[^[:alpha:][:space:]]*","",x)
corpus_sentim <- tm_map(corpus_sentim, content_transformer(remove_other))
corpus_sentim <- tm_map(corpus_sentim, content_transformer(removePunctuation))
corpus_sentim <- tm_map(corpus_sentim, content_transformer(tolower))
corpus_sentim <- tm_map(corpus_sentim, stripWhitespace)
corpus_sentim <- tm_map(corpus_sentim, stemDocument)

corpus_sentim <- corpus(corpus_sentim)
docnames_corpus_sentim <- docnames(corpus_sentim)

# For 7 sentiments
nrc_vector2 <- get_nrc_sentiment(corpus_sentim, language = "spanish")
str(nrc_vector2)

# We estimate the "sentiment" as "positive-negative"
nrc_vector2$sentiment <- nrc_vector2$positive-nrc_vector2$negative
str(nrc_vector2)

# let's add the name of the presidents
nrc_vector2$docnames_corpus_sentim <- docnames(corpus_sentim)
str(nrc_vector2)

# First, we graph the percentage of positive and negative words relative to each other. 
colors <- c("#E63D3D",#red 
            "#694DE6", #purple 
            "#196CFF", #blue
            "#3EA3B3", #aqua
            "#72C22B", #green
            "#4E9435",#green
            "#D4159F", #pink
            "#F59824", #orange
            "#631257", #burgundy
            "#717174") #gre

graph_prop_sentiment_ind <- barplot(
  sort(colSums(prop.table(nrc_vector2[, 9:10]))), # only positive and negative
  col = colors,
  horiz = TRUE, 
  cex.names = 0.7, 
  las = 1, 
  xlim = c(0,1),
  main = "Percentages of positive and negative sentiment
  in tweets individual's accounts (nrc dictionary)", xlab="Percentage"
  )

# Percentage of emotions in the tweets relative to each other
proportion_7_sentiment_ind <- colSums(prop.table(nrc_vector2[, 1:8]))

# Graph percentage of emotions in the text relative to each other
graph_prop_7_sentiment_ind <- barplot(
  sort(colSums(prop.table(nrc_vector2[, 1:8]))), # other sentiments 
  horiz = TRUE, 
  col = colors,
  cex.names = 0.7, 
  las = 1,
  main = "Percentages of emotions in tweets individual's accounts 
  (nrc dictionary)",
  xlim = c(0,0.4),
  xlab = "Percentage"
  )
