---
title: "Sandbox"
author: "Adelaida Barrera"
date: "11/30/2020"
output: html_document
---

# Trying to run topic model in full dfm 

```{r}

library(stm)

load("pruebas/full_feminists_dfm.RData")


#Make the quanteda dfm a stm corpus for running the model
stm_non_congress <- asSTMCorpus(non_congress_dfm)

# Getting info from the corpus
out <- prepDocuments(stm_non_congress$documents, 
                     stm_non_congress$vocab, 
                     stm_non_congress$meta)

# Running the structural topic model, defining 10 topics. 
model_topics_non_congress <- stm(documents = out$documents, 
              vocab = out$vocab, 
              K = 10, seed = 12345)

# Save the output for future plotting or analysis 
save(model_topics_non_congress, file = "model_topics_full")
```

#See what came out 

```{r}

plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = (1:3)) # or frex, lift, score
plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = (4:6)) 
plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = (7:9)) 
plot(model_topics_non_congress, type = "labels", labeltype = "prob", topics = 10)
 
```

#Trying scaling with wordfish 

```{r}


#Try the scaling with wordfish 

load("data/ind_tweets_on_politics")
load("data/non_congress_dfm_full")

manifestos <- distinct(tweets_on_politics) %>% group_by(screen_name) %>%
  filter(screen_name != "dianalzuleta") %>% 
  summarize(text = paste(text, collapse = " "))

manifestos_corpus <- corpus(x =  manifestos)

manifestos_dfm <- dfm(manifestos_corpus,
                       tolower = TRUE, # convert all words to lower case 
                      remove = c(stopwords("spanish")),
                      remove_punct = TRUE, # remove punctuation
                      remove_url = TRUE, # remove u
                      remove_numbers = TRUE,
                      remove_symbols = TRUE,
                      verbose = TRUE,
                      stem = T) # Bueno hacer esta opción para ver que está haciendo el dfm.
                #it is better not to stem for topic models  
             
# Remove mentions (@)
manifestos_dfm <- dfm_remove(manifestos_dfm,
                      "@*",
                      verbose = T)

#Remove hashtags         
manifestos_dfm <- dfm_remove(manifestos_dfm,
                      "#*",
                      verbose = T)

# Remove more stopwords (less than 3 characters)
manifestos_dfm <- dfm_keep(manifestos_dfm,
                    min_nchar = 3,
                      verbose = T)

manifestos_dfm <- dfm_trim(manifestos_dfm, min_termfreq = 5, verbose = TRUE)

wfish <- textmodel_wordfish(manifestos_dfm) 
#the 
summary(wfish)



```

```{r}
preds  <- predict(wfish, interval = "confidence")

# grab the (only) internal element 'fit' and make it a data frame

preds <- as_tibble(preds$fit)

preds_dv <- mutate(bind_cols(docvars(manifestos_dfm), preds),
                   user_order = rank(fit)) # add a left to right ordering

ggplot(preds_dv, aes(x = fit, xmin = lwr, xmax = upr,
                     y = user_order)) +
  geom_point() +
  geom_errorbarh(height = 0) +
   scale_y_continuous(labels = preds_dv$screen_name,
                     breaks = preds_dv$user_order) +
  theme_minimal() +
  labs(y = "",
       x = "Position",
       color = "",
       title = "Scale of latent ideological position",
       subtitle = "Based on tweets most likely to talk about the political topics")


```

```{r}


wscores <- tibble(word = wfish$features,
                  score = wfish$beta,
                  offset = wfish$psi)

wscores %>% arrange(score) %>% head(n = 50)
wscores %>% arrange(score) %>% tail(n = 50)
```




##### Otros métodos para limpiar y procesar el dfm
##### Otros métodos #####

mycorpus <- Corpus(VectorSource(feminists$text))
mycorpus <- tm_map(mycorpus, removeWords, stopwords("spanish"))

# Remove URL
remove_url <- function(x) gsub("http[^[:space:]]*","",x)
mycorpus <- tm_map(mycorpus, content_transformer(remove_url))

# Remove anything other than spanish letters and space
remove_other <- function(x) gsub("[^[:alpha:][:space:]]*","", x) 
mycorpus <- tm_map(mycorpus, content_transformer(remove_other))
mycorpus <- tm_map(mycorpus, content_transformer(removePunctuation))
mycorpus <- tm_map(mycorpus, content_transformer(tolower))
mycorpus <- tm_map(mycorpus, stripWhitespace)
mycorpus <- tm_map(mycorpus, stemDocument)

mycorpus <- corpus(mycorpus)
mycorpus_dfm <- dfm(mycorpus)

#Create a sample to try analysis 
sample_tm <- dfm_sample(x = mycorpus_dfm, size = 1000, margin = "documents")
